Final Presenation

### 2023-04-17 Final Presentation.Rmd

---
title: "Final Presenation"
author: "Siddhi Narayan"
date: "2023-04-16"
output: 
  ioslides_presentation:
    widescreen: true
    css: style.css
runtime: shiny
---

@@

## Distribution Over Time
* Plot - Line Graph of Citations by Race over Time
* Plot - Frequency of Citations vs. Hours in Day

## Distribution by Demographic
* Plot - Waffle Chart of Citation by Race 
* Plot - MPH over Speed Limit for Race/Gender

## Distribution by Location
* Plot - Citation by Sex by District 
* Table - Citations Per Square Mile

## 
table

## Killer 
<iframe src="http://127.0.0.1:5771" width="100%" height="500px"></iframe>

>>>>

---
title: "Final Presenation"
author: "Siddhi Narayan, Grace Wang, Virginia"
date: "2023-04-17"
output: 
  ioslides_presentation:
    widescreen: true
    css: style.css
runtime: shiny
---

@@

# Distribution Over Time
* Plot - Line Graph of Citations by Race over Time
* Plot - Frequency of Citations vs. Hours in Day

## Citation Count by Race over the Years
```{r Race/Year Line, message=FALSE}
source("subscripts/line_race_year.R", local=TRUE, print.eval=TRUE)
line_ry()
```

## Citation Frequency for Time of Day
```{r Time of Day Freq, message=FALSE}
source("subscripts/line_timeofcites.R", local=TRUE, print.eval=TRUE)
time_line()
```

# Distribution by Demographic
* Plot - Waffle Chart of Citation by Race 
* Plot - MPH over Speed Limit for Race/Gender

## Citation by Race
* How close is this to the truth?
```{r Waffle, message=FALSE}
source("subscripts/waffle.R", local=TRUE, print.eval=TRUE)
waffle()
```

## MPH over Speed Limit for Race & Gender {.smaller}
```{r Violin, message=FALSE}
source("subscripts/violin_speed.R", local=TRUE, print.eval=TRUE)
violin_speed()
```

# Distribution by Location
* Plot - Citation by Sex by District 
* Table - Citations Per Square Mile

## Citation by Sex by District
```{r Pyramid, message = FALSE}
source("subscripts/citation_pyramid.R", local = TRUE, print.eval = TRUE)
pyramid_cites()
```

## Citations Per Square Mile
* table

## Killer Plot
* Further breakdown Killer Plot by Police District
<iframe src="http://127.0.0.1:5771" width="100%" height="500px"></iframe>
